Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-04 Cover_letter_JPM.tex
Updates from Overleaf

*the authors should look for more data to verify these biomarkers.
???

@@

\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
%
we found that different expression value of gene SLC35E2.
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
% updated on 18-May-2021
\end{outline}

@@

% risk of 
Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.

>>>>

*the authors should look for more data to verify these biomarkers.
by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
or CPTAC (digital TMA, not HPA)
or more GEO datasets (GEO2837, GSE40774, GSE65858, GSE148944)

@@

\1 After investigation of mRNA expression dataset, the number of protein-coding genes in the TCGA HNSCC should be updated as 20500 (instead of 20499);
%
we found that different expression value of gene SLC35E2.
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
NCBI Reference Sequences (RefSeq)
According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A(Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities in TCGA HNSCC dataset.
% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
% keyword: (SLC35E2) AND "Homo sapiens" 
SLC35E2 is the previous symbols of SLC35E2A (Ref: https://www.genenames.org/data/gene-symbol-report/#!/hgnc_id/HGNC:20863).
We made reassignment of the expression value as SLC35E2A and SLC35E2B. % according to what?
% updated on 18-May-2021
\end{outline}

@@

% risk of 
Second, trying to find an optimal cutpoint of that \acrshort{rna} expression data to maximize candidate mining coverage, this strategy might identify more but weak "biomarkers". 
Thus, the false positives and adjustment of multiple comparisons should be corrected by \acrfull{fdr}.
And further validation of those candidate is required in the other independent dataset.% in larger patient populations.
%warrant.
